%% start of file `template_en.tex'.
%% Copyright 2007 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[10pt,letter]{moderncv}

% moderncv themes
\moderncvtheme[red]{classic}                               % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)

% character encoding
%\usepackage[]{inputenc}                                 % replace by the encoding you are using
\usepackage{fancyhdr}

\usepackage{color}
%\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}

% adjust the page margins
\usepackage[scale=0.9]{geometry}
\setlength{\hintscolumnwidth}{3.2cm}                     % if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths
\recomputelengths                                           % required when changes are made to page layout lengths

% personal data
\firstname{Andrew}
\familyname{Spott}
%\title{R\'esum\'e}                                    % optional, remove the line if not wanted
%\title{ }                                    % optional, remove the line if not wanted DAD SUGGESTS DROPPING RESUME
\address{Boulder, CO 80304}    % optional, remove the line if not wanted
% \mobile{415-596-3883}                                       % optional, remove the line if not wanted
% \email{andrew.spott (at) gmail (dot) com}                     % optional, remove the line if not wanted
% \homepage{spott.github.io}
\mobile{415-596-3883}                                       % optional, remove the line if not wanted
\email{andrew.spott (at) gmail (dot) com}                     % optional, remove the line if not wanted
%\homepage{spott.github.io}
%\extrainfo{additional information (optional)}              % optional, remove the line if not wanted
%\photo[64pt]{picture}                                      % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted
%\quote{Some quote (optional)}                              % optional, remove the line if not wanted

%\nopagenumbers{}                                           % uncomment to suppress automatic page numbering for CVs longer than one page
\pagestyle{fancy}
\chead{Andrew Spott}


%-----------------------------------------------------------
%            content
%-----------------------------------------------------------
\begin{document}

\maketitle
\vspace{-.7cm}
\thispagestyle{empty}
Broadly skilled Physics PhD and Data Scientist with over a decade of experience in scientific and mathematical computing.  
I like solving hard problems that generate strong business value.

\section{Experience}
\cventry{2021-}{Head of Data Science}{Submittable}{}{}{Submittable is a leader in the grant management space, 
helping projects succeed at launching, managing, and measuring their social impact projects.}
\cvline{$\diamond$}{\textbf{Projects}: I led the data science and auto-review efforts for the Working Washington Small Business Grant Program: Round 4 
and the Washington Covid-19 Immigrant Relief Fund projects.  We developed custom data analytics to allow these programs to optimize their funds' 
distribution, ensuring that money got to those with the most need according to their program goals.  We also developed the automatic review code 
which scored submissions according to rubrics provided by program leaders along with connecting to external data sources to validate submission information.  
Since this, I have been a key player in the solutioning for various larger enterprise deals, enabling data science and analytics services for our customers.}
\cvline{$\diamond$}{\textbf{Leadership}:  I lead our machine learning product team in the development of data products within the Submittable platform.  
I have operated as both the engineering manager, as well as the product manager, enabling the team to create great machine learning and data driven products.  
I also lead our customer data analytics platform intiative that is enabling our customers to better understand their project and their data from within our platform.}

\cvline{$\diamond$}{\textbf{Partnerships}:  Ideated and led the partnership that enabled a product known as Accelerated Review.  Accelerated Review is a custom 
machine learning modeling product to reduce review burdens for large projects.  Essentially we build a custom machine learning model using a smaller number of 
reviews and apply that model to review the rest of the submissions.}
%\cvline{$\diamond$}{\textbf{Product Management}:  }

\cventry{2017-2021}{Head of Data Science}{TruU Inc.}{}{}{TruU is a leading provider of passwordless authentication for the enterprise.  I spent three years building 
the data-science team and our initial behavioral biometrics.  I worked on everything within the data pipeline: from the initial development of our iOS application 
for data collection to the initial model development of our behavioral biometrics to the inference engine in production.}
\cvline{$\diamond$}{\textbf{Model Development}: I did the initial development of our gait biometric, which involved designing the data collection spec, developing 
the initial "walk/not-walk" model for what signals we would decide on, and developing the initial model using pytorch and deep learning.}
\cvline{$\diamond$}{\textbf{Datascience Support Infrastructure}: I managed our data science compute cluster for all data scientists, which was used for all 
research compute needs along with batch training for models in production.  I also wrote a large chunk of our internal deep learning library which among other 
things leveraged LMDB to enable easy use of out of memory data for training and ensure versioned models for reproducibility.}
\cvline{$\diamond$}{\textbf{Leadership}: I led a team of 2-4 data scientists in the development of two other biometrics, along with the continued development 
of the gait biometric.  This included technical advising, strategic planning and management.}
% \cvline{$\diamond$}{\textbf{Technical Skills}: I continually leverage my broad skillset to keep the data science team on track and progressing.  My IT skills have been used in the management of our local compute cluster.  I have used Python and Julia for general data analysis and model development, C++ for model deployment, and Swift for the initial data collection app development.  I have managed postgresql databases and used kibana to develop visualizations and dashboards for data collection monitoring.}

\cventry{2011--2017}{Research Assistant}{University of Colorado Boulder}{}{}{}
 \cvline{$\diamond$}{\textbf{Programming:  }Developed a non-trivial code to solve the time
   dependent Schr\"odinger equation (TDSE) in a field-free energy basis. 
   The code was developed using PETSc and Boost MPI in C++14, with an approximate size of 10kloc.}
 \cvline{$\diamond$}{\textbf{Data Analysis:  }Data analysis package for the above
   TDSE solver output. Developed using pandas, numpy, scipy and matplotlib.}

 \cventry{\phantom{2000--}2015}{Data Science Intern}{Cognilytics, Centurylink}{Denver}{}{}
 \cvline{$\diamond$}{\textbf{Data Science: } Preliminary analysis of anomalous
   network traffic for network security applications using raw packet captures with
   support vector machines, recurrent neural nets and random forests.}

 \cventry{2010--2017}{Teaching Assistant}{University of Colorado
   Boulder}{}{}{Taught a wide variety of introductory physics classes.
   Demonstrated a strong ability to take complex mathematical concepts and
   explain them intuitively.}
\pagebreak

\section{Education}
\cventry{2010--2017}{University of Colorado Boulder}{School of Arts and Sciences}{}{}{}
\cvline{$\diamond$}{\textbf{Ph.D.} Physics, \emph{Perturbative and
    ab-initio calculations of the electrical susceptibilities of atoms}}
\cvline{$\diamond$}{\textbf{Masters of Science} Physics, 2013}
\cventry{2004--2010}{University of Washington}{School of Arts and Sciences}{}{}{}
\cvline{$\diamond$}{\textbf{Bachelor of Science} Physics.}

\section{Side Projects}
\cventry{}{\textbf{A C++ wrapper around the C Library PETSc}}{}{}{}{}
\cvline{\textbf{petsc-cpp}}{\emph{https://github.com/spott/petsc-cpp}}
\cvline{$\diamond$}{An object oriented wrapper around PETSc for faster and safer
  PETSc development. The wrapper includes RAII types, operator overloading where
  it makes sense, and simpler interfaces to common tasks.}
% \cvline{\textbf{webpage-classifier}}{\emph{https://github.com/spott/webpage-classifier}}
% \cvline{$\diamond$}{A topic classifier for webpages,
%     developed in a literate style using reddit link posts as a
%     labeled data source.  Uses SQL, Docker, asyncio, and Latent Dirichlet
%     Analysis via gensim among other technologies.}

  %\section{Skills}
  % \cvline{\textbf{Python:}}{Comfortable with NumPy, SciPy, pandas and
  %   matplotlib.  Familiar with asyncio (including asyncpg and aiohttp), gensim and Scikit-Learn}
\cvline{\textbf{Data Science:}}{NumPy, SciPy, Pandas, Bokeh, Pytorch, Matplotlib}
\cvline{\textbf{Languages:}}{Python, C/C++/C++14, Swift, Julia, Bash/ZSH, SQL, Elasticsearch, LMDB}
%\cvline{\textbf{Other Languages:}}{Haskell, Mathematica}
%\cvline{\textbf{OS:}}{OS X, Unix/Linux, Windows}

\section{Selected Publications and Patents}
\cvline{US Patent }{\#US20220382845A1 \emph{Supervised and Unsupervised Techniques for Motion Classification}}
\cvline{2022}{\textbf{L. Budman, A. Agrawal, A. Spott}}

\cvline{US Patent }{\#US20200302722A1 \emph{Machine Learning-Based Platform For User Identification}}
\cvline{2021}{\textbf{L. Budman, A. Agrawal, A. Spott, M. Graf}}

\cvline{US Patent }{\#US20210248219A1 \emph{Integrated Quality Assessment for a Passive Authentication System}}
\cvline{2021}{\textbf{L. Budman, A. Agrawal, A. Spott, J. Carli}}

\cvline{US Patent }{\#US20220182379A1 \emph{Context-Based Risk Assessment for an Identity Verification System}}
\cvline{2021}{\textbf{L. Budman, A. Agrawal, O. Rodak, A. Spott}}

\cvline{US Patent }{\#US20210256789A1 \emph{Detecting Intent of a User Requesting Access to a Secured Asset}}
\cvline{2021}{\textbf{D. Pasirstein, J. Welch, A. Spott, L. Budman, A. Agrawal, N. Hacking}}

\cvline{Phys. Rev. A}{\emph{Time-dependent susceptibility of helium atom in intense laser pulses}}
\cvline{2017}{\textbf{A. Spott}, A. Jaron-Becker, and A. Becker}

\cvline{Phys. Rev. A}{\emph{Transition from perturbative to nonperturbative interaction in low-order-harmonic generation}}
\cvline{2015}{\textbf{A. Spott}, A. Becker, and A. Jaron-Becker}

\cvline{Phys. Rev. A}{\emph{Ab initio and perturbative calculations of the electric susceptibility of atomic hydrogen}}
\cvline{2014}{\textbf{A. Spott}, A. Jaron-Becker, and A. Becker}

\cvline{Optics Express}{\emph{Silicon-on-sapphire integrated waveguides for the mid-infrared} Optics Express}
\cvline{2010}{T. Baehr-Jones, A. Spott, R. Ilic, \textbf{A. Spott}, B. Penkov, W. Asher, and M. Hochberg}
 
% \section{Selected Presentations}
% \cvline{4 June 2014}{\emph{Theoretical analysis of the nonlinear susceptibility of hydrogen atom}}
% \cvline{}{45th Annual Meeting of the APS Division of Atomic, Molecular and Optical Physics, \textbf{Madison, WI}}
% \cvline{4 June 2013}{\emph{Numerical basis-state method for strong-field excitation and ionization}}
% \cvline{}{2013 Joint Meeting of the APS Division of Atomic, Molecular \& Optical Physics and the CAP Division of Atomic, Molecular \& Optical Physics, \textbf{Quebec City, Canada}}


%\closesection{}                   % needed to renewcommands
%\renewcommand{\listitemsymbol}{-} % change the symbol for lists

%\section{Extra 1}
%\cvlistitem{Item 1}
%\cvlistitem{Item 2}
%\cvlistitem[+]{Item 3}            % optional other symbol

%\section{Extra 2}
%\cvlistdoubleitem[\Neutral]{Item 1}{Item 4}
%\cvlistdoubleitem[\Neutral]{Item 2}{Item 5}
%\cvlistdoubleitem[\Neutral]{Item 3}{}

% Publications from a BibTeX file
\nocite{*}
\bibliographystyle{plain}
%\bibliography{publications}       % 'publications' is the name of a BibTeX file

\end{document}


%% end of file `template_en.tex'.
